---
title: "Horse Racing - Sport Betting Modelling"
author: "Xihang Chen"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    number-sections: true
    theme: cosmo
    code-fold: true
execute:
  echo: true
  warning: false
  message: false
  cache: false
params:
  seed: 42
  edge_threshold: 0.05
  data_path: "input/horse_racing_dataset.xlsx"
---

## Set up

```{r}
set.seed(params$seed)

library(dplyr)
library(readxl)
library(here)
library(lubridate)
library(tibble)
library(ggplot2)
library(splines)
library(glmnet)
library(broom)
library(lubridate)

source(here::here("helpers.R"))

df <- readxl::read_excel("input/horse_racing_dataset.xlsx")
```

## Overall summary
This project develops a race-level win probability model for horse racing using a conditional logit framework that accounts for the competitive structure within each race. The model incorporates performance ratings for horses, jockeys, and trainers, alongside race-level features (distance, going, field size, race type), and tests whether these variables improve prediction after accounting for Betfair Starting Price (BSP). Performance is evaluated out-of-sample using probabilistic metrics (log loss, Brier score, calibration) and simulated betting returns with confidence intervals, with a focus on economically meaningful residual edge.

## Data Exploration
The dataframe consists of following columns:
```{r}
colnames(df)
```
Upon inspection, `obs_completion_time` is missing primarily for non-completions (UR, PU, BD, etc.), with `obs_racing_post_rating` following the same pattern. Missingness is therefore outcome-dependent rather than random, reflecting structural censoring. These variables are excluded from predictive modelling to avoid leakage and bias.

## Implementation of Rating Systems
I constructed a forward-looking rating system for each entity (i.e., horses, jockeys and trainers) separately using `obs_racing_post_rating`. For each entity at each race, I aggregated only prior runs and computed a time-decayed weighted mean of past ratings, thus recent performances contribute more than older ones. I then applied empirical Bayes-style shrinkage towards the global ratings. This ensures ratings were stable, leakage-safe, and avoids overreacting to small sample sizes.

```{r}
df <- df %>%
  make_td_shrinkage_rating(
    id_col = "horse_id",
    half_life_days = 180,  # faster-changing form
    k = 8,
    out_col = "rating_horse_td"
  )
```